Verifying Demonstrations

### 2018-11-23 paper/adversary-model.tex
Clarifies the adversary

There are three players: the protest participant (with identity) \(P\), a 
witness (with identity) \(W\) and the storage \(S\).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

@@

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary controls \(W\) and \(S\); the adversary thus learns everything 
  that they do, but can also correlate what he learns from \(W\) and \(S\).
  \(W\) and \(S\) only learn the protocol data --- no auxiliary data.

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.

@@

One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous 
communication.
However, given a strong enough adversary, such anonymous communication might not be possible.
We capture such a strong adversary as \cref{deanonymizing-adversary}.

>>>>

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

@@

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data (such as who sent it).

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  %(\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still learns only the protocol data, no auxiliary data.

@@

As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
control the channel between \(P\) and \(S\), \eg when \(P\) uses 
Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
jurisdiction.

However, given a strong enough adversary, such anonymous communication might 
not be possible; \eg if the adversary can do a time-correlation attack.
We capture such a strong adversary as \cref{deanonymizing-adversary}.
